Modeling the impacts of replacing car trips with combined public transport and cycling: Reproducible methods, results and actionable evidence from biclaR

### 2024-05-08 paper/PaperCEUS/PaperCEUS_rev1.Rmd
matsim ref

# plot 1
ggplot(data = CAR_PT_TRANSF_mun_or_geo_18) +
  geom_sf(aes(fill = Bike_new10)) +
  viridis::scale_fill_viridis(option = "G", direction = -1, name = "Bike + PT trips", na.value = "white") +
  theme_void()
  # theme(legend.position = "bottom") +
  # labs(title = "Potential Bike + PT for 10% target, by municipality")

@@

Table \ref{tab:summary22} presents emissions reductions and associated economic benefits associated with the second (PT) leg of trips.
The shift from private car associated with thes PT segments would reduce CO~2~ equivalent emissions by 8,500 to 20,800 tons annually, valued in €1.4 million to €3.5 million yearly, for the 4% and 10% targets, respectively.

@@

## Generalizability and limitations

@@

A strength of the approach is that there is no requirement for sensitive individual trip level data to reproduce the approach in other cities.
However, we acknowledge that this approach has limitations.
The approach cannot show exactly which trips are being replaced, in terms of the age of people making the trips, the types of car they drive, and other individual or vehicle level variables.
We assumed uniformity in the type of vehicle for all replaced car journeys, albeit with variations in the fuels utilized.
Additionally, we assumed consistency in the health impacts across all individuals for the replaced car trips.
This approach is a simplification of reality to enable the analysis of a large region on available computing resources.
Future work could seek to increase the resolution of the results, and move towards a more individual-level analysis, for example by using agent and activity-based models using tools such as MATSim.
This direction of travel would require substantial resources outside the scope of this study; another way to improve the spatial resolution of results would be to use higher resolution 'subpoints' as the basis of the desire line 'jittering' process.
We would also like to explore the potential for probabilistic routing to improve the spatial resolution of the results.

>>>>

# plot 1
ggplot(data = CAR_PT_TRANSF_mun_or_geo_18_extrap) +
  geom_sf(aes(fill = Bike_new10)) +
  viridis::scale_fill_viridis(option = "G", direction = -1, name = "Bike + PT trips", na.value = "white") +
  theme_void()
  # theme(legend.position = "bottom") +
  # labs(title = "Potential Bike + PT for 10% target, by municipality")

@@

The benefits are spatially unevenly distributed across the LMA, as shown in Figure \ref{fig:mapzones}.

<!-- The potential of the intermodality scenario is not only in the number of trips that can be made, but also in the potential to reduce emissions and improve the quality of life in the LMA. -->
Table \ref{tab:summary22} presents emissions reductions and associated economic benefits associated with the second (PT) leg of trips.
The shift from private car associated with thes PT segments would reduce CO~2~ equivalent emissions by 8,500 to 20,800 tons annually, valued in €1.4 million to €3.5 million yearly, for the 4% and 10% targets, respectively.

@@

# Generalizability and limitations

@@

A strength of the approach is that there is no requirement for sensitive individual trip level data to reproduce the approach in other cities.
However, we acknowledge that this approach has limitations.
The approach cannot show exactly which trips are being replaced, in terms of the age of people making the trips, the types of car they drive, and other individual or vehicle level variables.
We assumed uniformity in the type of vehicle for all replaced car journeys, albeit with variations in the fuels utilized.
Additionally, we assumed consistency in the health impacts across all individuals for the replaced car trips.
This approach is a simplification of reality to enable the analysis of a large region on available computing resources.
Future work could seek to increase the resolution of the results, and move towards a more individual-level analysis, for example by using agent and activity-based models using tools such as MATSim [@MATSim].
This direction of travel would require substantial resources outside the scope of this study; another way to improve the spatial resolution of results would be to use higher resolution 'subpoints' as the basis of the desire line 'jittering' process.
We would also like to explore the potential for probabilistic routing to improve the spatial resolution of the results.

### 2024-05-08 paper/PaperCEUS/PaperCEUS_rev1.tex
imptove map 3
matsim ref

{\centering \includegraphics[width=0.6\linewidth,]{img/map1}

@@

@@

\subsection{Model replicability and
limitations}\label{model-replicability-and-limitations}

This paper focus primarily on the potential of making cycling and PT a
viable alternative to car trips, and the socio-environmental benefits of
such a shift.

This analysis can be applied to other metropolitan areas, providing a
basis for decision-making and policy development to support a modal
shift from car to PT. This process involves a minimum of data
requirements, such as the origin-destination data, road network, and the
PT GTFS data, which are available in most metropolitan areas.
Furthermore, it is essential to incorporate existing cycling level
targets specific to those areas or consider the possibility of utilising
the same targets as outlined in the Portuguese national strategy, in
order to compare results with different areas.

@@

A strength of the approach is that there is no requirement for sensitive
individual trip level data to reproduce the approach in other cities.
However, we acknowledge that this approach has limitations in terms of
being able to identify exactly which trips are being replaced -- in
terms of the age of people making the trips, the types of car they
drive, and other individual or vehicle level variables. We assumed
uniformity in the type of vehicle for all replaced car journeys, albeit
with variations in the fuels utilized. Additionally, we assumed
consistency in the health impacts across all individuals for the
replaced car trips This approach is a simplification of the real-world
scenario, but it is a necessary one to make the analysis feasible and
reproducible.

A further refinement could be to differentiate between `simpler'
no-transfer PT trips (which require less person effort) and more arduous
multi-transfer PT trips, using the same methods, by relaxing the
assumption of no-transfers between PT modes in \texttt{r5r}. This would
led to a larger number of total daily trips that can be made by cycling
+ PT, in particular in locations where the PT network is less complex
and requires more transfers. We could also set a different maximum
lenght of cycling stage, extending the bicycle catchment area. However,
despite the added value of a sensibility analyses, they would also
increase the overall complexity, and would have an impact on the
explainability of the results to be used by policy makers.

>>>>

{\centering \includegraphics[width=0.6\linewidth,]{PaperCEUS_rev1_files/figure-latex/map1-1}

@@

The benefits are spatially unevenly distributed across the LMA, as shown
in Figure \ref{fig:mapzones}.

@@

\section{Generalizability and
limitations}\label{generalizability-and-limitations}

This paper focus primarily on the potential for replacing trips
currently made by car with combined cycling and public transport trips,
and the associated social and environmental benefits. While the results
are specific to the Lisbon Metropolitan Area, the approach is designed
to be generalizable to other metropolitan areas.

An important aspect of the approach from a generalizability perspective
is that it has specific data requirements, including origin-destination,
road network, and the GTFS data. Such datasets are available to
transport planners in many areas. In areas where such datasets do not
exist, the value of research such as this could provide a motivation to
collect and open-up transport data. For this study we have used
Portugal's national cycling targets as the basis of the scenarios; the
approach can be adapted to other targets, or to other policy goals, such
as reducing congestion or improving air quality.

@@

A strength of the approach is that there is no requirement for sensitive
individual trip level data to reproduce the approach in other cities.
However, we acknowledge that this approach has limitations. The approach
cannot show exactly which trips are being replaced, in terms of the age
of people making the trips, the types of car they drive, and other
individual or vehicle level variables. We assumed uniformity in the type
of vehicle for all replaced car journeys, albeit with variations in the
fuels utilized. Additionally, we assumed consistency in the health
impacts across all individuals for the replaced car trips. This approach
is a simplification of reality to enable the analysis of a large region
on available computing resources. Future work could seek to increase the
resolution of the results, and move towards a more individual-level
analysis, for example by using agent and activity-based models using
tools such as MATSim \citep{MATSim}. This direction of travel would
require substantial resources outside the scope of this study; another
way to improve the spatial resolution of results would be to use higher
resolution `subpoints' as the basis of the desire line `jittering'
process. We would also like to explore the potential for probabilistic
routing to improve the spatial resolution of the results.

A further refinement could be to differentiate between `simpler'
no-transfer PT trips (which require less person effort) and more arduous
multi-transfer PT trips, using the same methods, by relaxing the
assumption of no-transfers between PT modes in the routing engine. This
would led to a larger number of total daily trips that can be made by
cycling + PT, in particular in locations where the PT network is less
complex and requires more transfers. We could also set a different
maximum lenght of cycling stage, extending the bicycle catchment area.
However, despite the added value of a sensibility analyses, they would
also increase the overall complexity, and would have an impact on the
explainability of the results to be used by policy makers.
